\begin{thebibliography}{1}
% Unused:
% M. D. Ercegovac and T. Lang. Digital Arithmetic

\bibitem{Ahmed1}
  I. Ahmed, S. Zhao, J. Meijers, O. Trescases and V. Betz,
  ``\textit{Automatic BRAM Testing for Robust Dynamic Voltage Scaling for
  FPGAs}'',
  \textit{Int. Conf. on Field-Programmable Logic and Applications},
  2018.

\bibitem{Amin1}
  A Amin, W. Shinwari,
  ``\textit{High-Radix Multiplier-Dividers: Theory, Design, and Hardware}'',
  \textit{IEEE Trans. Comput.}, vol. 1, no.8,
  2008.

\bibitem{Brent1}
  R.P. Brent,
  ``\textit{A Regular Layout for Parallel Adders}'',
  \textit{IEEE Trans. Comput.}, vol. C-31, pp. 260-264,
  1982.

\bibitem{Catanzaro1}
  B. Catanzaro, and B. Nelson,
  ``\textit{Higher Radix Floating-Point Representations for FPGA-Based
  Arithmetic}'',
  \textit{Proceedings of the 51st Annual Design Automation Conference},
  2005.

\bibitem{Chen1}
  L. Chen, F. Lombardi, P. Montuschi, J. Han and W. Liu,
  ``\textit{Design of Approximate High-Radix Dividers by Inexact Binary
  Signed-Digit Addition}'',
  \textit{Proceedings of the on Great Lakes Symposium on VLSI},
  2017.

\bibitem{Duncan1}
  R. Duncan,
  ``\textit{A Survey of Parallel Computer Architectures}'',
  \textit{Computer}, vol. 23, pp. 5-16,
  1990.

\bibitem{Duran1}
  J.W. Duran,
  ``\textit{An Evaluation of Random Testing}'',
  \textit{IEEE Trans. on Software Engineering}, vol. SE-10, no. 4, pp. 438-444,
  1984.

\bibitem{Ercegovac1}
  M.D. Ercegovac,
  ``\textit{On-line Arithmetic: An Overview}'',
  \textit{28th Annual Technical Symposium}, pp. 86-93,
  Internaltional Society for Optics and Photonics,
  1984.

\bibitem{Ercegovac2}
  M.D. Ercegovac, and T. Lang,
  ``\textit{Digital Arithmetic}'',
  Morgan Kaufmann,
  2003.

\bibitem{Hazwani1}
  S. Hazwani, et al,
  ``\textit{Randomness Analysis of Pseudo Random Noise Generator Using 24-bits
  LFSR}'',
  \textit{Fifth Int. Conf. on Intelligent Systems, Modelling and Simulation},
  2014.

\bibitem{Kornerup1}
  P. Kornerup,
  ``\textit{Reviewing High-Radix Signed-Digit Adders}'',
  \textit{IEEE Trans. Comput.}, vol.64, no. 5, pp. 1502-1505,
  2015.

\bibitem{Li1}
  H. Li, J.J. Davis, J. Wickerson and G.A. Constantinides,
  ``\textit{ARCHITECT: Arbitrary-precision Constant-hardware Iterative
  Compute}'',
  \textit{Int. Conf. on Field-Programmable Technology},
  2017.

\bibitem{Lynch1}
  T. Lynch, and M.J. Schulte,
  ``\textit{A High Radix On-line Arithmetic for Credible and Accurate
  Computing}'',
  \textit{Journal of Universal Computer Science}, vol. 1, no. 7, pp. 439-453,
  1995.

\bibitem{Lynch2}
  T. Lynch, and M.J. Schulte,
  ``\textit{Software for High Radix On-line Arithmetic}'',
  \textit{Reliable Computing}, vol. 2, no. 2, pp. 133-138,
  1996.

\bibitem{Srinivas1}
  H.R. Srinivas, and K.K. Parhi,
  ``\textit{High-Speed VLSI Arithmetic Processor Architectures Using Hybrid
  Number Representation}'',
  \textit{J. of VLSI Sign. Process.}, vol. 4. pp. 177-198,
  1992.

\bibitem{Shi1}
  K. Shi, D. Boland, and G.A. Constantinides,
  ``\textit{Accuracy-Performance Tradeoffs on an FPGA through Overclocking}'',
  \textit{Proc. Int. Symp. Field-Programmable Custom Computing Machines},
  pp. 29-36,
  2013.

\bibitem{Shi2}
  K. Shi, D. Boland, E. Stott, S. Bayliss, and G.A. Constantinides,
  ``\textit{Datapath Synthesis for Overclocking: Online Arithmetic for
  Latency-Accuracy Trade-offs}'',
  \textit{Proceedings of the 13th Symposium on Field-Programmable Custom
  Computing Machines},
  pp. 1-6, ACM,
  2014.

\bibitem{Scekic1}
  O. Šćekić
  ``\textit{FPGA Comparative Analysis}'',
  \textit{University of Belgrade},
  2005.

\bibitem{Tenca1}
  A.F. Tenca, and M.D. Ercegovac,
  ``\textit{Design of high-radix digit-slices for on-line computations}'',
  2007.

\bibitem{Trivedi1}
  K.S. Trivedi, and M.D. Ercegovac,
  ``\textit{On-line Algorithms for Division and Multiplication}'',
  \textit{IEEE Trans. Comput.}, vol. C-26, no. 7, pp. 667-680,
  1977.

\bibitem{Whyte1}
  P. Whyte,
  ``\textit{Design and Implementation of High-radix Arithmetic Systems Based
  on the SDNR/RNS Data Representation}''
  \textit{Edith Cowan University},
  1997.

\bibitem{Zhao1}
  Y. Zhao, J. Wickerson, and G.A. Constantinides,
  ``\textit{An Efficient Implementation of Online Arithmetic}'',
  \textit{Int. Conf. on Field-Programmable Technology},
  2016.

% ------------------------------------------------------------------------------

\bibitem{Accellera1}
  Accellera Systems Initiative,
  ``\textit{Universal Verification Methodology 1.2 User’s Guide}'',
  2015.
  % Available at:\\\url{https://accellera.org/images/downloads/standards/uvm/
  % uvm_users_guide_1.2.pdf}.

\bibitem{Altera1}
  Altera Corporation,
  ``\textit{Cyclone V SoC Development Board Reference Manual}'',
  2015.
  % Available at:\\\url{www.intel.com/content/dam/www/programmable/us/en/pdfs/
  % literature/manual/rm_cv_soc_dev_board.pdf}.

\bibitem{Altera2}
  Altera Corporation,
  ``\textit{Memory System Design}'',
  \textit{Embedded Design Handbook},
  2010.
  % Available at:\\\url{www.intel.com/content/dam/www/programmable/us/en/pdfs/
  % literature/hb/nios2/edh_ed51008.pdf}.

\bibitem{Altera3}
  Altera Corporation,
  ``\textit{Introduction to Altmemphy IP}'',
  \textit{External Memory Interface Handbook: Reference Material}, vol. 3,
  2012.
  % Available at:\\\url{www.intel.com/content/dam/www/programmable/us/en/pdfs/
  % literature/hb/external-memory/emi_ddr3_ug.pdf}

\bibitem{Altera4}
  Altera Corporation,
  ``\textit{Phase-Locked Loop Basics, PLL},''.
  % Available at:\\\url{https://www.intel.com/content/www/us/en/programmable/
  % support/support-resources/operation-and-testing/pll-and-clock-management/
  % pll-basics.html}

\bibitem{Altera5}
  Altera Corporation,
  ``\textit{Creating Qsys Components}'',
  2018.
  % Available at:\\\url{https://www.intel.com/content/dam/www/programmable/us/
  % en/pdfs/literature/hb/qts/qsys_components.pdf}.

\bibitem{Altera6}
  Altera Corporation,
  ``\textit{Cyclone V Hard Processor System Technical Reference Manual}'',
  2018.
  % Available at:\\\url{https://www.intel.com/content/dam/www/programmable/us/
  % en/pdfs/literature/hb/cyclone-v/cv_54005.pdf}.

\bibitem{Imperial1}
  Imperial College
  ``\textit{An Ethics Code}'',
  \textit{Imperial College Research Ethics Committee},
  2013.

\bibitem{Intel1}
  Intel Corporation,
  ``\textit{Cyclone V SoC Development Kit and Intel SoC FPGA Embedded
  Development Suite}''.
  % Available at:\\\url{www.intel.com/content/www/us/en/programmable/products/
  % boards_and_kits/dev-kits/altera/kit-cyclone-v-soc.html}.

\bibitem{Intel2}
  Intel Corporation,
  ``\textit{Introduction to Intel FPGA IP Cores}'',
  2018.
  % Available at:\\\url{https://www.intel.com/content/www/us/en/programmable/
  % documentation/mwh1409960636914.html}.

\bibitem{Intel3}
  Intel Corporation,
  ``\textit{Avalon Interface Specifications}'',
  2018.
  % Available at:\\\url{https://www.intel.com/content/dam/www/programmable/us/
  % en/pdfs/literature/manual/mnl_avalon_spec.pdf}.

\bibitem{Rocket1}
  RocketBoards.org,
  ``\textit{GSRD 14.1 User manual}'',
  2015.
  % Available at:\\\url{https://rocketboards.org/foswiki/Documentation/GSRD141}.

\bibitem{Xilinx1}
  Xilinx, Inc,
  ``\textit{Zynq-7000 All Programmable SoC}'',
  2018.
  % Available at:\\\url{www.xilinx.com/support/documentation/
  % product-briefs/zynq-7000-product-brief.pdf}.

\bibitem{Xilinx2}
  Xilinx, Inc,
  ``\textit{ZedBoard (Zynq Evaluation and Development) Hardware User's Guide}'',
  2012.
  % Available at:\\\url{https://reference.digilentinc.com/_media/
  % zedboard:zedboard_ug.pdf}.
\end{thebibliography}