\section{Ethical, Legal and Safety Plan}
% The Ethical, Legal and Safety Plan must detail what are the issues in this are
% relevant to your project, showing how you will comply with best practice. If
% there are no such issues (the case for 80\% of all projects) you must
% nevertheless show here that you have considered these issues and detail why they
% will not apply to your project. Information will be provided on the project web
% pages about Ethical, Legal and Safety matters.

\subsection{Ethical Considerations}
% Ethics: Research projects are required to get ethical approval if they may have
% issues. It is not at all usual for EEE FYPs to have such issues, but you should
% be aware of the possibility, most usually relating to personal data when you
% conduct questionnaires or do user testing.

Checking against the ethical issue list provided by Imperial College Research
Ethics Committee~\cite{Imperial1}, this project does not
\begin{itemize}
  \item damage participants' mental or physical health;
  \item jeopardise the safety or liberty of the researchers;
  \item use any private information;
  \item involve sensitive subject matter or methods;
  \item risk any conflict of interest between the researchers and the College.
\end{itemize}
This project is thus free from significant ethical concerns.

\subsection{Legal Considerations}
% Legal issues: the obvious one here is patent protection. Your work may infringe
% patents (which does not affect the project itself, but might affect
% commercialisation). You are not required to do a patent search but should be
% aware of the possibility if you have a deliverable that could be commercialised.
% Also, your work may (if it goes well) be patentable. You can usually check this
% with your supervisor. If so you will need to ensure that nothing you do
% prejudices this possibility. There may also be regulatory issues with
% electromagnetic radiation.
Intel Quartus Prime software offers a variety of IP cores.
These are encrypted module designs that can be integrated into the
verification system of the project~\cite{Intel2}.
This project integrates some of these IP cores so that some of the basic
circuit building blocks does not need to be redesigned.

While it is possible to complete this project with a free licence,
Imperial has academic licences for the software allowing for faster
compilation time.
This licence also allows these IPs to be used for research purposes.
As this product is academic, the licence is appropriate and sufficient.
This project therefore, has no legal issues.

\subsection{Safety Considerations}
% Safety: check with your supervior (who is ultimately responsible for safety in
% your lab work). Also, you can get information from the lab staff - e.g. Vic
% Boddy - about possible safety issues in the lab. Note that Vic is not
% responsible for safety, though quite knowledgable, so you must also check this
% with your supervisor. Many projects will have no lab work and therefore no
% safety issues.
As the development board used does not have high voltages, there is no safety
issues in this project.
A detailed safety analysis is available as a separate document.